{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-12 brains-protocol.tex
Redo list of psycholinguitic indices + refs

%In order to start bridging this gap, we set out to \emph{empirically} study public representation transformations at the microscopic level; 
%aiming to stay compatible with macroscopic-level studies of these public representations.
In practice, quotations appeared indeed to be a perfect candidate for designing a first \emph{in vivo} measure of low-level cognitive bias in a reformulation task. % as public representations.
First, they are usually cleanly delimited by quotation marks %(and often with HTML markup in web pages), 
which greatly facilitates their detection in text corpora.
Second, they stem from a unique ``original'' version, and could ideally be traceable back to that version.
Third, and most importantly, their duplication should \emph{a priori} be highly faithful, apart from cases of cropping: not only should transformations be of moderate magnitude, but when specific words are not perfectly duplicated, it is safe to assume that the variation is due to involuntary cognitive bias --- as writers may expect any casual reader to easily verify, and thus criticize, the fidelity to the original quotation.

We therefore examine transformation processes by comparing the substituted and substituting words. To keep the analysis palatable, we focused on quotation transformations consisting of the \emph{substitution} of a word by another word (and only those cases) in order to unambiguously discuss single word replacements. 
To quantify those substitutions, we decided to associate a number of features to each word, the variation of which we can statistically study.
The next subsections describe the dataset and measures we used to assess this cognitive bias.
%Quotation evolution is therefore a perfect environment to measure cognition-induced transformations.%and relate those findings to macroscopic social dynamics.

@@

We now introduce some of the most classical psycholinguistic measures on words.
\rk{Add some bibliography about those features' known effects}

\begin{itemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, \rk{add ref on why it's important}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary,
    \item The average \textbf{Number of Synonyms} for all meanings of a word, obtained from WordNet~\citep{WordNet10}. \rk{add ref on why it's important}
\end{itemize}

>>>>

%In order to start bridging this gap, we set out to \emph{empirically} study public representation transformations at the microscopic level; 
%aiming to stay compatible with macroscopic-level studies of these public representations.
Quotations appeared to be a perfect candidate to propose a first \emph{in vivo} measure of low-level cognitive bias in a reformulation task. % as public representations.
First, they are usually cleanly delimited by quotation marks %(and often with HTML markup in web pages), 
which greatly facilitates their detection in text corpora.
Second, they stem from a unique ``original'' version, and could ideally be traceable back to that version.
Third, and most importantly, their duplication should \emph{a priori} be highly faithful, apart from cases of cropping: not only should transformations be of moderate magnitude, but when specific words are not perfectly duplicated, it is safe to assume that the variation is due to involuntary cognitive bias --- as writers may expect any casual reader to easily verify, and thus criticize, the fidelity to the original quotation.

We could therefore examine the individual substitution process at work when authors transform quotations, by examining the features of the substituted and substituting words in each substitution. To keep the analysis palatable, we focused on quotation transformations consisting in the \emph{substitution} of a word by another word (and only those cases) in order to unambiguously discuss single word replacements. 
To quantify those substitutions, we decided to associate a number of features to each word, the variation of which we can statistically study.

The next subsections describe the dataset and measures we used to assess this cognitive bias.
%Quotation evolution is therefore a perfect environment to measure cognition-induced transformations.%and relate those findings to macroscopic social dynamics.

@@

We now introduce some of the most classical psycholinguistic measures on words.

\begin{itemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, known to be relevant for both recognition and recall~\citep{gregg1976word},
    \item \textbf{Age of Acquisition}: the average age at which words are learned (obtained from~\citet{kuperman12}), known to have different effects than word frequency~\citep{morrison1995roles,dewhurst1998separate},
    \item The average \textbf{Number of Phonemes} and \textbf{Number of Syllables} for all pronunciations of a word (obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98})\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.} as a proxy to word production cost,
    \item The average \textbf{Number of Synonyms} for all meanings of a word (obtained from WordNet~\citep{WordNet10}) as a proxy to word polysemy.
\end{itemize}
